Where and Why Does the Model Failed? A Visual Analytics Tool for Debugging and Interpreting Text Entailment Model

### 2018-02-22 paper/intro.tex
minor fixes

The key contributions of the proposed works is summarized as the following:
\begin{itemize}
    \item Allow user to quickly identify the mistakes made by the model through input perturbation and visual summerization;

    \item Introduce visual encoding for interpreting the attention that incorporate sentence linguistic structure;

    \item Interactively explore the relationship between attention and prediction via constrained optimization
\end{itemize}

>>>>

The key contributions of the proposed works is summarized as the following:
\begin{itemize}
    \item Identify the mistakes made by the model through perturbation of input sentences and visual summarization of the predictions;

    \item Enhance the visual representation of attention by overlaying sentence linguistic structure to allow grammar guided simplification;

    \item Enable the interrogation of the attention mechanism by interactively exploring how the change in prediction affect the attention and vice versa while fixing other part of the model

\end{itemize}

### 2018-02-22 paper/paper_entailVis.tex
minor fixes

%% Abstract section.
% What are we doing in this paper
\abstract{
With the recent advances of deep learning, neural network based models have reset
the state-of-the-art for nearly all linguistic tasks in natural language
processing. The disruptive advance also brings enormous challenges.
The opaque nature of neural network model leads to hard to debug system and
difficult to interpret mechanism~cite{}. In this work, we use textual
entailment task as an example to illustrate how a flexible visualization
system can help NLP researchers quickly identify the potential limitation of
a models and interpret the model inner states for make sense of the attention mechanism.
} % end of abstract

>>>>

%% Abstract section.
% What are we doing in this paper
\abstract{
With the recent advances in deep learning, neural network based models have reset the state-of-the-art performance for nearly all linguistic tasks in natural language processing. The disruptive progress also brings enormous challenges.
The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms. In this work, we use textual entailment task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a model, but also facilitate the interpretation the model mechanisms by allowing interactive exploration of the interplay between model input, attention, and the prediction.
} % end of abstract
